---
title: "Credit card Fraud detection"
output:
  html_notebook: default
  word_document: default
  pdf_document: default
---

importing libraries and data
```{r}
library(ranger)
library(caret)
library(data.table)
data <- read.csv("C:\\Users\\rishu\\Desktop\\Credit_card_fraud\\Activity-2_CCFD\\creditcard.csv")
```
exploration
```{r}
data.table(data)

```
summary of amount

```{r}
summary(data$Amount)
sd(data$Amount)
IQR(data$Amount)
var(data$Amount)
```
manipulation

```{r}
data$Amount<- scale(data$Amount) #normalization

data2<- data[,-c(1)] #removing time from data
head(data2)

set.seed(12)
library(caTools)

sample_data <- sample.split(data2$Class,SplitRatio=0.80)

train_data <- subset(data2,sample_data==TRUE)
test_data <- subset(data2,sample_data==FALSE)

dim(train_data)
dim(test_data)
```

Training and fitting logistic model

glm function is used to fit the mode (Generalized Linear Models)

Syntax: 
glm(formula, family = gaussian, data, weights, subset,
    na.action, start = NULL, etastart, mustart, offset,
    control = list(…), model = TRUE, method = "glm.fit",
    x = FALSE, y = TRUE, singular.ok = TRUE, contrasts = NULL, …)
    
```{r}
Logistic_model1 <- glm(Class~.,train_data,family=binomial())
summary(Logistic_model1)

plot(Logistic_model1)

```

Efficiency of the Logistic Regression by ROC curve

```{r}
library(pROC)
lr.predict <- predict(Logistic_model1,test_data,probability = TRUE)
auc.gb <- roc(test_data$Class,lr.predict,plot=TRUE,col="green")
```

so we have max 90% accuracy but it is not right method of doing project

So
we try fitting a decision tree

rpart: Recursive Partitioning and Regression Trees

syntax:
rpart(formula, data, weights, subset, na.action = na.rpart, method,
      model = FALSE, x = FALSE, y = TRUE, parms, control, cost, …)


```{r}
library(rpart)
library(rpart.plot)

desicion_model <- rpart(Class ~ . , data,method = "class")
predicted_val <- predict(desicion_model,data,type="class")
probability <- predict(desicion_model,data,type='prob')
rpart.plot(desicion_model)
```
